?????????????????

### 2022-12-05 article_1/Result1.tex
Replace apsg library with mplstereonet

\begin{figure}[hbpt]
\centering
\includegraphics[width=1.0\textwidth]{ComplexStereo.png}
\caption{a) The real data models a thin section of rock with particles uniformly magnetized in the average direction of the induced field 45\textdegree/45\textdegree. b) The recovered data, without any type of filtering, are sparse, but statistically generate the same average direction. (c) It is still possible to filter only the directions of the magnetic sources with the best fitting determined by the coefficient of determination (e.g., $R^ 2 \geq 0.7$) to ensure better grouping of the directions around the mean value.}
\label{fig:ComplexSynthetic3}
\end{figure}

>>>>

\begin{figure}[hbpt]
\centering
\includegraphics[width=1.0\textwidth]{ComplexStereo.png}
\caption{a) The real data models a thin section of rock with particles uniformly magnetized in the average direction of the induced field 45\textdegree/45\textdegree. b) The recovered data, without any type of filtering, are sparse, but statistically generate the same average direction. c) It is still possible to filter only the directions of the magnetic sources with the best fitting determined by the coefficient of determination (e.g., $R^ 2 \geq 0.7$) to ensure better grouping of the directions around the mean value.}
\label{fig:ComplexSynthetic3}
\end{figure}
